---
title: "Index"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: yeti
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(spotifyr)
library(tidyverse)
library(ggplot2)
```

### Meet Death Grips

**Death Grips** is an experimental hiphop band with three members. When I got introduced to their music, I hated it. However, after torturing myself for quite some time, it grew on me. Their music is extremely energetic and, if I might say so, quite aggressive. I have not always been able to put my finger on Death Grips’ music. In most of their songs, there is so much happening at the same time: when I think I have found the rhythm, it changes again. Therefore, I am very curious what the Spotify API would make out of Death Grips' music. The goal of this research is to analyze their music and by that, find out how Death Grips' music changed over time.

*The Money Store* (2012) is their most popular album. In total, they released 8 albums, including one instrumental album and a mixtape. I chose to exclude the mixtape *Exmilitary*, because it is not on Spotify (it includes uncleared samples). And just so it has been mentioned: one of these seven albums is actually a double album. Next to the seven remaining albums, I will include their EP *Death Grips*. This EP is an instrumental one. Therefore, it will be valuable to expand my data. Like mentioned before, I want to compare the different albums throughout the years. I will be focussing on the following questions:

- What makes Death Grips so experimental and inaccessible? How can we distinguish this ‘experimentalness’ with the data gained from Spotify’s API?
- Is their most popular music their least experimental music?
- How did Death Grips' music change over time? Has Death Grips become more experimental over time?

In summary, I will be analyzing i) how Death Grips changed over time and ii) what makes Death Grips experimental. My research will be based on the data of 7 albums and 1 EP.
```{r}
```

### Too energetic?

``` {r plots}
library(tidyverse)
library(spotifyr)
library(dplyr)
corpus <- get_playlist_audio_features("", "6BoVVeeH3vmrHlgivNbefW")

corpus_new <- corpus 
ggplot(data = corpus_new, aes(x = track.album.name, y  = energy)) +
  geom_boxplot(fill = "#00abff") +
  labs(x = "",
    y = "energy" ,
    title = "Energy per album" ,
    subtitle = "",
    caption = "Data source: Spotify API") +
  theme_minimal() +
  theme(
    title = element_text(color = "gray25"),
    plot.caption = element_text(color = "gray25"),
    axis.text.x = element_blank()) +
    coord_flip()
```

***

Before making this plot, I expected the energy levels of Death grips' music to be high. I think their music is very energetic, sometimes even too energetic for me. Maybe this is what makes the music experimental and inaccessible. 

We can see very clearly that every album has a very high mean of energy, since every box is on the far right of the plot.

Funny enough, there is one dot at far left. Apparently there is a song on *Interview 2016* which is consequently Death Grips' least energetic song. 

Also, *No Love Deep Web* is quite an outlier compared to the energy levels of the rest of the albums. The median energy of this album is the lowest of all. This is their second released album. Maybe they thought they needed to refrain themselves. Wait a minute, they are **Death Grips**. They definitely did not held back on purpose.

Their music did not get less or more energetic over time. ???

So, we can state that the remarkable high energy levels of Death Grips' music is part of what makes it experimental. This will help in researching whether their most popular music their least experimental music.

### Most popular song

```{r compus chromagram}
remotes::install_github('jaburgoyne/compmus')
library(tidyverse)
library(spotifyr)
library(compmus)
getgot <-
  get_tidy_audio_analysis("781V2Y5LPtcpgONEOadadE") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)
getgot %>%
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) %>%
  compmus_gather_chroma() %>% 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c()
```

***

This chromagram is made from the song *Get Got*, Death Grips' most popular song.

### Conclusion

```{r}

```

